Summary of the things that I learned

### 2024-09-28 100-introduction.tex
Add a lot of references to the code

>>>>

Note that throughout this document, links are included to \href{https://arnoudvanderleer.github.io/cs-masters-thesis/toc.html}{\nolinkurl{documentation}} of the corresponding formalized material. The documentation refers to the state of \href{https://github.com/UniMath/UniMath/tree/5eb5c8958c4dddd4219f895bf7bc51547395522d}{\nolinkurl{the UniMath repository}} at commit number \texttt{5eb5c8958c4dddd4219f895bf7bc51547395522d}.
